\begin{thebibliography}{9}
\bibitem{loadTesting} 
Tse-Hsun Chen, Mark D. Syer, Weiyi Shang, Zhen Ming Jiang, Ahmed E. Hassan, Mohamed Nasser, and Parminder Flora.
\textit{Analytics-Driven Load Testing: An Industrial Experience Report on Load Testing of Large-Scale Systems.}. 
In ICSE-SEIP '17; 243-252.
 
\bibitem{bugLocalization} 
Saha RK, Lease M, Khurshid S, Perry DE.
\textit{Improving bug localization using structured information retrieval.}.
 In ASE, 2013; 345–355.
 
\bibitem{deepLog} 
Min D, Feifei L, Guineng Z, Vivek S. 
\textit{DeepLog: Anomaly Detection and Diagnosis from System Logs through Deep Learning.}.
In ACM SIGSAC, Conference on Computer and Communications Security(CCS), 2017; 1285-1298.

\bibitem{survey} 
Tse-Hsun Chen, Stephen W. Thomas, Ahmed E. Hassan
\textit{A Survey on the Use of Topic Models when Mining Software Repositories}.
Empirical Software Engineering, 2016, Volume 21, Number 5, Page 1843

\bibitem{trbLocalization} 
Chris Mills, Jevgenija Pantiuchina, Esteban Parra, Gabriele Bavota, Sonia Haiduc
\textit{Are Bug Reports Enough for Text Retrieval-based Bug Localization?}.
ICSE'18 Proceedings of the 40th International Conference on Software Engineering: Companion Proceeedings, Pages 248-249 

\bibitem{replicationASF}
Boyuan Chen, Zhen Ming (Jack) Jiang
\textit{Characterizing logging practices in Java-based open source software projects – a replication study in Apache Software Foundation}
Empirical Software Engineering, 2017, Volume 22, Number 1, Page 330-374.

\end{thebibliography}